Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-01-24 paper_comparison/paper_comparison/paper_comparison.Rmd
results on the fitted value distributions

Surprisingly, the visual test rejects `r nr$n[1]` out of `r nr$n[1]+nr$n[2]` (`r round(nr$n[1]/(nr$n[1]+nr$n[2])*100, 0)`%) of lineups where the conventional test does not reject. Figure \ref{fig:heter-example} shows this lineup. The data plot in position seventeen displays a relatively strong heteroskedasticity pattern, and has a strong effect size ($log_e E=4.02$). This is reflected by the visual test $p\text{-value} = 0.026$, but the Breusch-Pagan test $p\text{-value} = 0.056$, slightly above the significance cutoff of $0.05$. This lineup was evaluated by 11 subjects, it has experimental factors $n=50$ (small sample size), $\sigma=1$, and a uniform distribution for the fitted values. It must be the small sample size that may have resulted in the lack of detection.

@@

Although the distribution of the regressor is classically not restricted by the assumptions of linear regression, it will have an impact on the fitted value distribution and the visual effect of the residual plot. In our experiments, four distributions of fitted values are considered to accommodate this variation.

>>>>

Surprisingly, the visual test rejects `r nr$n[1]` of the `r nr$n[1]+nr$n[2]` (`r round(nr$n[1]/(nr$n[1]+nr$n[2])*100, 0)`%) of lineups where the conventional test does not reject. Figure \ref{fig:heter-example} shows this lineup. The data plot in position seventeen displays a relatively strong heteroskedasticity pattern, and has a strong effect size ($log_e E=4.02$). This is reflected by the visual test $p\text{-value} = 0.026$, but the Breusch-Pagan test $p\text{-value} = 0.056$, slightly above the significance cutoff of $0.05$. This lineup was evaluated by 11 subjects, it has experimental factors $n=50$ (small sample size), $\sigma=1$, and a uniform distribution for the fitted values. It must be the small sample size that may have resulted in the lack of detection.

@@

The prediction in a regression model is $E(Y|X)$, that is, it is conditional on observed values of the predictors. The distribution of $X$, or consequently $\hat{Y}$, may however affect the ability to read any patterns in the residuals. <!-- Although the distribution of the regressor is classically not restricted by the assumptions of linear regression, it will have an impact on the fitted value distribution and the visual effect of the residual plot.--> The four distributions of fitted values, used in this experiment, were designed to examine this.

### 2023-01-24 paper_comparison/paper_comparison/paper_comparison.tex
results on the fitted value distributions

Surprisingly, the visual test rejects 1 out of 33 (3\%) of lineups where
the conventional test does not reject. Figure \ref{fig:heter-example}
shows this lineup. The data plot in position seventeen displays a
relatively strong heteroskedasticity pattern, and has a strong effect
size (\(log_e E=4.02\)). This is reflected by the visual test
\(p\text{-value} = 0.026\), but the Breusch-Pagan test
\(p\text{-value} = 0.056\), slightly above the significance cutoff of
\(0.05\). This lineup was evaluated by 11 subjects, it has experimental
factors \(n=50\) (small sample size), \(\sigma=1\), and a uniform
distribution for the fitted values. It must be the small sample size
that may have resulted in the lack of detection.

@@

Although the distribution of the regressor is classically not restricted
by the assumptions of linear regression, it will have an impact on the
fitted value distribution and the visual effect of the residual plot. In
our experiments, four distributions of fitted values are considered to
accommodate this variation.

>>>>

Surprisingly, the visual test rejects 1 of the 33 (3\%) of lineups where
the conventional test does not reject. Figure \ref{fig:heter-example}
shows this lineup. The data plot in position seventeen displays a
relatively strong heteroskedasticity pattern, and has a strong effect
size (\(log_e E=4.02\)). This is reflected by the visual test
\(p\text{-value} = 0.026\), but the Breusch-Pagan test
\(p\text{-value} = 0.056\), slightly above the significance cutoff of
\(0.05\). This lineup was evaluated by 11 subjects, it has experimental
factors \(n=50\) (small sample size), \(\sigma=1\), and a uniform
distribution for the fitted values. It must be the small sample size
that may have resulted in the lack of detection.

@@

The prediction in a regression model is \(E(Y|X)\), that is, it is
conditional on observed values of the predictors. The distribution of
\(X\), or consequently \(\hat{Y}\), may however affect the ability to
read any patterns in the residuals. The four distributions of fitted
values, used in this experiment, were designed to examine this.
